\chapter{Background}
\label{ch:background}

When looking at the history of online education for Old Dominion University specifically, the institution's distance learning efforts predate the internet, starting in the mid-1980s\cite{oduglobal:history} with courses offered on U.S. Navy ships deployed around the globe. These first iterators were built on the institution's original satellite delivery program, TELETECHNET\cite{585174}, which was officially established in 1994. TELETECHNET used satellites to transmit classroom broadcasts from the main campus in Norfolk, Virginia, to partner sites around the country in the form of interactive television. 

In an effort to facilitate offline asynchronous learning, the Department of Engineering Management \& Systems Engineering at Old Dominion University started offering their courses to U.S. Navy submarine sailors
\footnote{\url{https://online.odu.edu/master-engineering-management-mem-portable-media-course-list}}. This method was made possible by delivering course content for offline consumption using CD-ROMs and a binder of paper resources such as user guides. This way of educating is still in place, and CD-ROMs are getting delivered on a semester-pre-semester basis to students in need. The TELETECHNET delivery of courses was used until 2014, when the institution's distance learning efforts were moved to the web. 

While institutions around the country were moving to the web, the method of teaching and the content being delivered to the students remained the same. Courses were being taught synchronously and asynchronously, but the instructors delivered the same course content to all students regardless of their strengths and limitations. 

In 2023, personalized content is not a new concept, as for the past decade, algorithmic content has been delivered to us in the form of advertisements, recommendations, and search results. The question is, \textbf{have we adapted our educational platforms and delivery methods to societal changes in how emerging technologies have shaped the past two decades}?