\chapter{Module Clustering System}
\label{ch:mcs}

The system comprises five main segments, each responsible for their respective duties. Preprocessing of raw text features was a necessary step in order to normalize the characters present in the sample space. Stop word removal, word stemming, text transformations, POS tagging, and tokenization are all part of the preprocessing steps. However, they vary based on the document embedder used in the later step. Regarding the document embedder, the project was tested with two different methods. One is TF-IDF text vectorization, a standard but legacy method of representing text in a vector space. This had its drawbacks which will be discussed in the architecture section of this report. The second method of document embedding implemented is using Open AI's GPT-3.5 model, which significantly improved the accuracy of our clustering and allowed us to remove most of the preprocessing steps. This was done since the GTP model has context awareness, and removing words from documents would have mangled the natural speech pattern extracted from transcripts and other text features. After either document embedding method is run, an unsupervised clustering algorithm predicts the cluster to assign the module to. The outputted clusters are referred to as Collections in the sense of the “course structure.” For each predicted cluster, we utilized the GPT-3.5 DaVinci model for completion and input our prompt to generate learning outcomes. The prompt used for completion is as follows: “You are the instructor of the course, broken into clusters of videos. Based on the clustering inputted, generate ten learning outcomes, for each cluster, based on the commonality that they share between contents.” Finally, a JSON structure is outputted, representing the path the student must take to gain accreditation in a specific course. This path is then validated and used cosine similarity, comparing the offered structure with the ground truth inputted from the database. This is in place so we do not present students with a path that resembles the exact structure used in the ground truth, as this is most likely not the most optimal way of finishing the course.
